Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-13 HGmodelMANUSCRIPT/coverLETTER.tex
Update coverLETTER.tex

\documentclass[12pt]{letter}
\usepackage{graphicx,baskervald,microtype}
\usepackage{hyperref,amsmath,xcolor}
\usepackage{pgfplots,marginnote}
\usepackage[top=0.5in,bottom=0.5in,left=1in,right=1in]{geometry}
%\newgeometry{margin=2.5cm}
\newcommand{\omamargin}[1]{\marginnote{\textbf{#1}}[7pt]}
\begin{document}
\reversemarginpar
\pagestyle{empty}
\noindent O. H. Samuli Ollila \\
\noindent Helsinki Biophysics and Biomembrane Group\\
\noindent Department of Biomedical Engineering and Computational Science\\
\noindent P.O. Box 12200, FI-00076 Aalto University, Espoo, Finland\\
\noindent samuli.ollila@aalto.fi, Tel. +358503746963, Fax. +358 9 470 23182 \\

@@

In addition to its main message, the manuscript also provides an extensive comparison on the quality of the head group 
structures of numerous widely used lipid models in varying biologically relevant conditions. The behavior
of the lipid head group region plays a key role in multiple processes, such as partitioning of drugs or 
nanoparticles into membranes and interactions of peripheral proteins with membranes, both of which are 
currently intensively studied. Therefore the manuscript provides crucial information for a large group
of computational scientists who are struggling to select the best possible lipid model for the problem at hand.

>>>>

\documentclass[11pt]{letter}
\usepackage{graphicx,baskervald,microtype}
\usepackage{hyperref,amsmath,xcolor}
\usepackage{pgfplots,marginnote}
\usepackage[top=0.5in,bottom=0.5in,left=1in,right=1in]{geometry}
%\newgeometry{margin=2.5cm}
\newcommand{\omamargin}[1]{\marginnote{\textbf{#1}}[7pt]}
\begin{document}
\reversemarginpar
\pagestyle{empty}
\noindent O. H. Samuli Ollila \\
\noindent Helsinki Biophysics and Biomembrane Group\\
\noindent Department of Biomedical Engineering and Computational Science\\
\noindent P.O. Box 12200, FI-00076 Aalto University, Espoo, Finland\\
\noindent samuli.ollila@aalto.fi, Tel. +358503746963, Fax. +358 9 470 23182 \\

@@

In addition to its main message, the manuscript also provides an extensive comparison on the quality of the head group 
structures of numerous widely used lipid models in varying biologically relevant conditions. The behavior
of the lipid head group region plays a key role in multiple processes, such as partitioning of drugs or 
nanoparticles into membranes and interactions of peripheral proteins with membranes, both of which are 
currently intensively studied. Therefore the manuscript provides crucial information for a large group
of computational scientists who are struggling to select the best possible lipid model for their research.
